Balsa: A Compact Line Notation Based on SMILES

### 2022-07-31 manuscript.tex
Qualifies atomic index. Closes #43

Broader expansion of Balsa's capabilities could be possible through \textit{metaformats}. A metaformat embeds one or more Balsa strings within a surrounding serialization format. For example, two- or three-dimensional coordinates could be associated with each atom through a metaformat that includes a dictionary mapping atomic index to coordinate. Collections of atoms or bonds could likewise be encoded to replicate the enhanced stereochemistry features of other formats. And so on. However, the utility of such extensions should be weighed against Balsa's main value proposition: high information density. An application attempting to use a verbose metaformat may benefit from adopting better-suited format instead.

>>>>

Broader expansion of Balsa's capabilities could be possible through \textit{metaformats}. A metaformat embeds one or more Balsa strings within a surrounding serialization format. For example, two- or three-dimensional coordinates could be associated with each atom through a metaformat that includes a dictionary mapping implicit atomic index to coordinate. An implicit atomic index could in turn be based on node order. Collections of atoms or bonds could likewise be encoded to replicate the enhanced stereochemistry features of other formats. And so on. However, the utility of such extensions should be weighed against Balsa's main value proposition: high information density. An application attempting to use a verbose metaformat may benefit from adopting better-suited format instead.
